Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-08-27 Documents/Paper/ms.tex
Going through paper, added Stephens reference

\section{Introduction}\label{sec:introduction}
\setlength{\parindent}{0cm}
\setlength{\parskip}{3mm}
Many inference problems have the following structure. There is some unknown
number, $N$, of objects in a region. Each of the $N$ objects has a property
$\xx$, which may be a single scalar value (for example, a mass), or a set of
values (e.g. a two-dimensional position and a mass). These problems are often
challenging due to the unknown (and potentially large) dimensionality.

To do the inference, we must assign a prior to the objects' properties
$\{\xx_i\}_{i=1}^N$.
Since $N$ may be large, it is usually easier to assign an ``interim prior''
conditional on some hyperparameters $\hyperparams$, and then assign a prior to
$\hyperparams$. This kind of model is usually called {\it hierarchical}.
The prior for $N$, $\hyperparams$, and $\{\xx_i\}$ is usually factorised
in the following way:

@@

Here we have assumed the priors for $N$ and $\hyperparams$ are independent, and
the interim prior for $\{\xx_i\}$ is iid and does not depend on $N$.
Given data $\mathcal{D}$, we usually want to calculate properties of the
posterior distribution given by:
\begin{eqnarray}
p(N, \hyperparams, \{\xx_i\} | \mathcal{D}) \propto
p(N, \hyperparams, \{\xx_i\})
p(\mathcal{D} | N, \hyperparams, \{\xx_i\})\label{eq:bayes}
\end{eqnarray}
The general method used to calculate properties of the posterior distribution
is to generate samples from it using Markov Chain Monte Carlo (MCMC). The
structure of the model is depicted graphically in Figure~\ref{fig:pgm}.

@@

>>>>

\section{Introduction}\label{sec:introduction}
\setlength{\parindent}{0cm}
\setlength{\parskip}{3mm}
Consider the following class of inference problems. There is some unknown
number, $N$, of objects in a (physical or metaphorical) region. Each of the $N$ objects has a property
$\xx$, which may be a single scalar value (for example, a mass), or a set of
values (e.g. a two-dimensional position and a mass). These problems are often
challenging to solve due to the unknown (and potentially large) dimensionality.

To carry out the inference, we must assign a prior to the objects' properties
$\{\xx_i\}_{i=1}^N$.
Since $N$ may be large, it is usually easier to assign an ``interim prior''
conditional on some hyperparameters $\hyperparams$, and then assign a prior to
$\hyperparams$. This kind of model is usually called {\it hierarchical}.
The prior for $N$, $\hyperparams$, and $\{\xx_i\}$ is usually factorised
in the following way:

@@

Here we have assumed the priors for $N$ and $\hyperparams$ are independent, and
the interim prior for $\{\xx_i\}$ is iid and does not depend on $N$.
Given data $\mathcal{D}$, we usually want to calculate properties of the
posterior distribution, given by:
\begin{eqnarray}
p(N, \hyperparams, \{\xx_i\} | \mathcal{D}) \propto
p(N, \hyperparams, \{\xx_i\})
p(\mathcal{D} | N, \hyperparams, \{\xx_i\})\label{eq:bayes}
\end{eqnarray}
The structure of the model is depicted graphically in Figure~\ref{fig:pgm}.

The computational method used to calculate properties of the posterior distribution
is to generate samples from it using Markov Chain Monte Carlo (MCMC). Since
$N$ is unknown, an MCMC sampler needs to be able to jump between candidate
solutions with different numbers of objects, using either birth-death MCMC
\citep{birthdeath} or the reversible jump framework of \citet{rjmcmc}.

@@

\bibitem[Stephens(2000)]{birthdeath} Stephens, M., 2000, ``Bayesian analysis of mixture models with an unknown number of components-an alternative to reversible jump methods.'', Annals of Statistics (2000), 40-74.
